### 2020-04-20 final_report/methodology.tex
add two more subsections
reorder words in table
add outline for supervised learning experiments

\begin{table}[h]
	\centering
	\begin{tabular}{llrl}
	\toprule
	Regression performance metrics	& Mathematical formulation / description &
	\multicolumn{2}{c}{Ideal value} \\
	\midrule
	Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
								& [TBR] \\
	Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
	\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
	$R^2$ (coefficient of determination)	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
	Adjusted $R^2$	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 & [rel.] \\
	\midrule
	Evaluation time metrics	& {} & {} & {} \\
	\midrule
	Mean training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
	$\hat{f}(x)$})/N_0$ 	& 0 & [ms] \\
	Mean prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
	$\hat{f}(x)$})/N$	& 0 & [ms] \\
	Relative speedup	& $(\text{wall evaluation time of $f(x)$}) /
	(N\overline{t}_{\text{pred.}})$	&
	$\to\infty$ & [rel.] \\
	\bottomrule
	\end{tabular}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}

@@

\subsection{Model Comparisons}
\label{sec:model}

>>>>

\begin{table}[h]
	\centering
	\begin{tabular}{llrl}
	\toprule
	Regression performance metrics	& Mathematical formulation / description &
	\multicolumn{2}{c}{Ideal value} \\
	\midrule
	Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
								& [TBR] \\
	Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
	\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
	Coefficient of determination $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
	Adjusted $R^2$	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 & [rel.] \\
	\midrule
	Evaluation time metrics	& {} & {} & {} \\
	\midrule
	Mean training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
	$\hat{f}(x)$})/N_0$ 	& 0 & [ms] \\
	Mean prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
	$\hat{f}(x)$})/N$	& 0 & [ms] \\
	Relative speedup	& $(\text{wall evaluation time of $f(x)$}) /
	(N\overline{t}_{\text{pred.}})$	&
	$\to\infty$ & [rel.] \\
	\bottomrule
	\end{tabular}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}

@@

\subsection{Supervised Learning Experiments}
\label{sec:supervised}

\subsubsection{Considered Surrogates}

\begin{table}[h]
	\centering
	\begin{tabular}{llll}
	\toprule
	Surrogate & Acronym & Implementation & Hyperparameters \\
	\midrule
	Support vector machines	& SVM & SciKit Learn & TODO \\
	Gradient boosted trees	& GBT & SciKit Learn & TODO \\
	Extremely random trees	& ERT & SciKit Learn & TODO \\
	AdaBoost	& AB & SciKit Learn & TODO \\
	Gaussian process regression	& GPR & SciKit Learn & TODO \\
	$k$ nearest neighbours	& KNN & SciKit Learn & TODO \\
	Neural networks	& NN & Keras (TensorFlow) & TODO \\
	Inverse distance weighing & IDW & SMT & TODO \\
	Radial basis functions & RBF & SMT & TODO \\
	Stochastic gradient descent & SGD & SciKit Learn & TODO \\
	Ridge regression & RR & SciKit Learn & TODO \\
	Kriging & KRG & SMT & TODO \\
	\bottomrule
	\end{tabular}
	\caption{TODO}
	\label{tbl:surrogates}
\end{table}

TODO: describe classes of surrogates

TODO: reference implementations and original papers

TODO: define NN architectures

\subsubsection{Experiments}

TODO: single slice hyperparameter optimisation

TODO: multislice (mixed) hyperparameter optimisation

TODO: retraining for scaling benchmark

TODO: retraining on large set
